eba_sims_data

### 2020-02-17 src/eba_sims_w_data.Rmd
update file

```{r setup, echo = FALSE}
setwd("~/eba_sims/src")
library(ggplot2)
library(gridExtra)
library(knitr)
library(plyr)
library(lubridate)
library(numbers)
library(data.table)
library(R.utils)
library(forecast)
source("pffunctions.R")
```

@@

```{r}
dons <- dons[with(dons, order(date)), ]
firsts <- dons[!duplicated(dons$donor),]
```

```{r}
firsts[1:20,]
```

```{r}
counts <- data.frame()
weeks <- c()
for (i in 1:dim(firsts)[1]) {
  stamp <- paste0(year(firsts[i,]$date), '.', week(firsts[i,]$date))
  if(!(stamp %in% weeks)){
    weeks <- c(weeks, stamp)
    counts[stamp, "Count"] <- 1
  }
  else{
    counts[stamp, "Count"] <- counts[stamp, "Count"] + 1
  }
}
```

```{r}
ggplot(data = counts, aes(x=row.names(counts), y=Count)) + 
  geom_point(color = "dark red") +
  theme(axis.text.x = element_text(angle = 45)) +
  scale_x_discrete(breaks=c("2010.1", "2011.1", "2012.1", "2013.1", "2014.1", "2015.1", "2016.1", "2017.1", "2018.1", "2019.1")) +
  theme_bw() +
  labs(title = "Number of weekly first time donations",
       subtitle = "Assuming 2010 as anomalous, the weekly donations fall to the 500 range with small seasonality.",
       x = "Weeks",
       y = "Count")
```

>>>>

```{r setup, echo = FALSE}
setwd("~/eba_sims/src")
library(ggplot2)
library(gridExtra)
library(knitr)
library(dplyr)
library(plyr)
library(lubridate)
library(numbers)
library(data.table)
library(R.utils)
library(forecast)
source("pffunctions.R")
```

@@

```{r}
# Function to transfrom dates to year.week 
yearweek <- function(x = Sys.Date()) {
  xday <- ISOdate(year(x), month(x), day(x), tz=tz(x))
  dn <- 1 + (wday(x) + 5)%%7
  nth <- xday + ddays(4 - dn)
  jan1 <- ISOdate(year(nth), 1, 1, tz=tz(x))
  return(sprintf("%s.%d", format(nth, "%Y"), 1 + (nth - jan1)%/%ddays(7)))
}
```

```{r}
# Order donations by date
dons <- dons[with(dons, order(date)), ]

# Transform dates to yearweeks
dons$date <- yearweek(dons$date)

# Extract first time donations
firsts <- dons[!duplicated(dons$donor),]
```

```{r}
# Check
firsts[1:20,]
```
```{r}
# Attempting vectorization of the processes below

# Firsts
first_count <- as.data.frame(table(factor(firsts$date, levels=unique(firsts$date))))
# (We needed to call factor() to retain the chronological order of the rows)
colnames(first_count) <- c("week", "firsts")

# All
all_count <- as.data.frame(table(factor(dons$date, levels=unique(dons$date))))
colnames(all_count) <- c("week", "all")
```

```{r}
# Combine into one neat df
counts_df <- data.frame(week=first_count$week, 
                        first=first_count$firsts, 
                        all=all_count$all)
```

```{r}
# Plot
ggplot(data = counts_df, aes(x=week, y=first)) + 
  geom_point(color = "dark red") +
  geom_point(aes(x=week, y=all), color = "pink") +
  theme(axis.text.x = element_text(angle = 45)) +
  geom_abline(intercept = mean(counts_df[158:520,2]), slope=0) +
  geom_abline(intercept = mean(counts_df[158:520,3]), slope=0) +
  scale_x_discrete(breaks=c("2010.1", "2011.1", "2012.1", "2013.1", "2014.1", "2015.1", "2016.1", "2017.1", "2018.1", "2019.1")) +
  theme_bw() +
  labs(title = "Number of weekly first time donations vs. all donations",
       subtitle = paste0("Each week around ", round(mean(counts_df[158:520,2])/mean(counts_df[158:520,3])*100, 2), "%", " of all donations comprise first time donors (2013 onwards)."),
       x = "Weeks",
       y = "Count") +
  annotate(geom="text", 
           x="2019.1", 
           y=mean(counts_df[158:520,2])+400, 
           label=paste0("Firsts: ", round(mean(counts_df[158:520,2]), 1))) +
  annotate(geom="text",
           x="2019.1",
           y=mean(counts_df[158:520,3])+400, 
           label=paste0("All: ", round(mean(counts_df[158:520,3]), 1)))
```
